---
output: pdf_document

---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```



# QF112.  Homework #2.


## `r format(Sys.time(), "%Y-%m-%d")`

I pledge my honor that I have abided by the Stevens Honor System.

By filling out the following fields, you are signing this pledge.  No assignment will get credit without being pledged.

Name:

CWID:

Date:




```{r}
CWID = -1 #Place here your Campus wide ID number, this will personalize
#your results, but still maintain the reproduceable nature of using seeds.
#If you ever need to reset the seed in this assignment, use this as your seed
#Papers that use -1 as this CWID variable will earn 0's so make sure you change
#this value before you submit your work.
personal = CWID %% 10000
set.seed(personal)
```

It will be up to you to determine where you should use R code in this document.  You can easily add a new section of code by simply using copy/paste or typing it in yourself.  For your convenience, a blank section of code is provided below.

```{r}
# my response
```

# Question 1

For this question, you will need to choose two assets and download the daily adjusted close for the last (calendar) year.  Save this data as a csv and then read it in as a data frame.  You will use this data to do the following:

## a) 

For each of your assets, find the sample mean and sample standard deviation of your data.

## b)

Create a histogram for each asset, showing each in its own plot. 

## c)

Create a box-plot for each asset

## d)

Determine the sample covariance and sample correlation coeffecient for these two assets.


# Question 2 (Adapted from Stinerock: Statistics with R)

Using the Cars93 data (which can be found in the MASS package)
## a)
Print out the variable names
## b)
For the Type variable, print out the frequency and relative frequency tables.  Using these tables, what percentage of the data set are large cars?
## c)
Create a cross-tabulation table of the variables Origin and Type.  Using this table, can you conclude that most of the vehicles are of US origin?



# Question 3 (Adapted from Stinerock: Statistics with R)

Using the LakeHuron data set (already in R), find the range, interquartile range, variance, standard deviation, and coeffecient of variation.







