---
output: pdf_document

---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```



# QF112.  Homework #6.


## `r format(Sys.time(), "%Y-%m-%d")`

I pledge my honor that I have abided by the Stevens Honor System.

By filling out the following fields, you are signing this pledge.  No assignment will get credit without being pledged.

Name:

CWID:

Date:




```{r}
CWID = -1 #Place here your Campus wide ID number, this will personalize
#your results, but still maintain the reproduceable nature of using seeds.
#If you ever need to reset the seed in this assignment, use this as your seed
#Papers that use -1 as this CWID variable will earn 0's so make sure you change
#this value before you submit your work.
personal = CWID %% 10000
set.seed(personal)
```

It will be up to you to determine where you should use R code in this document.  You can easily add a new section of code by simply using copy/paste or typing it in yourself.  For your convenience, a blank section of code is provided below.

```{r}
# my response
```

# Question 1 

For this problem, you will be using your previous data set of the two assets that you downloaded.

## a)

Do these assets have a net day to day increase the majority of the time?  Choose your own significance level that you feel will be relevant for this question.

## b)

Is the standard deviation of the simple returns for each asset greater than .015?  Again choose a level of significance that you feel is relevant.




# Question 2 (Adapted from Stinerock)

Doctors in Tampa reportedly earn an average salary of 141,300 dollars.  We conduct a survey of doctors in New Orleans with a sample of size $n=64$ to test whether their mean salary is different from that in Tampa and get the result that our sample mean is 138,000 dollars.

## a)

If we assume that $\sigma=18,000$, at the level of $\alpha=.01$ use the six-step framework to test whether the true mean in New Orleans is different from that of Tampa.

## b)

What is the $p$-value?

## c)

If we assume that $\sigma=18,000$, at the level of $\alpha=.01$ use the six-step framework to test whether the true mean in New Orleans is less than that of Tampa.

## d)

If the true mean in New Orleans is actually 139,000 dollars, what is the $\beta$ of this test?

# Question 3 (Adapted from Probability and Statistics for Engineers and Scientest by Walpole Myers Myers and Ye)

Based on past experiences, a professor believes that the time that it takes students to complete a test is a random variable with mean 35 minutes.  If a random sample of 20 students is taken that has a sample average time of 33.1 minutes with standard deviation 4.3, at the .05 significance level, should the professor determine that the true mean is actually less than the 35?


