---
output: pdf_document

---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```



# QF112.  Homework #1.


## `r format(Sys.time(), "%Y-%m-%d")`

I pledge on my honor that I have not given or received any unauthorized assistance on this assignment/examination. I further pledge that I have not copied any material from a book, article, the Internet or any other source except where I have expressly cited the source.

By filling out the following fields, you are signing this pledge.  No assignment will get credit without being pledged.

Name:

CWID:

Date:




```{r}
CWID = -1 #Place here your Campus wide ID number, this will personalize
#your results, but still maintain the reproduceable nature of using seeds.
#If you ever need to reset the seed in this assignment, use this as your seed
#Papers that use -1 as this CWID variable will earn 0's so make sure you change
#this value before you submit your work.
personal = CWID %% 10000
set.seed(personal)
```
# Question 1

Use R to calculate the square root of 30



```{r}
#response
```


# Question 2

What is 34.6 multiplied by 23.5

```{r}
# my response
```

# Question 3

Create a vector of the first 10 elements of the Fibonacci sequence, starting with 0

```{r}
# my response
```

# Question 4

Create a data frame consisting of the first 10 elements of the Fibonacci sequence as well as their index in the sequence.  Name the columns appropriately.

```{r}
# my response
```


