---
output: pdf_document

---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```



# QF112.  Homework #5.


## `r format(Sys.time(), "%Y-%m-%d")`

I pledge my honor that I have abided by the Stevens Honor System.

By filling out the following fields, you are signing this pledge.  No assignment will get credit without being pledged.

Name:

CWID:

Date:




```{r}
CWID = -1 #Place here your Campus wide ID number, this will personalize
#your results, but still maintain the reproduceable nature of using seeds.
#If you ever need to reset the seed in this assignment, use this as your seed
#Papers that use -1 as this CWID variable will earn 0's so make sure you change
#this value before you submit your work.
personal = CWID %% 10000
set.seed(personal)
```

It will be up to you to determine where you should use R code in this document.  You can easily add a new section of code by simply using copy/paste or typing it in yourself.  For your convenience, a blank section of code is provided below.

```{r}
# my response
```

# Question 1 

For this problem, you will be using your previous data set of the two assets that you downloaded.

## a)

For the first asset, determine the 60%, 90%, and 95% confidence intervals for the population mean of the adjusted close prices.

## b)


For the first asset, restrict your data set to just the most recent two weeks.  Use only this data to determine the 60%, 90%, and 95% confidence intervals for the population mean of the adjusted close prices.

## c)

For the second asset, determine the 60%, 90%, and 95% confidence intervals for the population variance.

## d)

After converting your second asset to the log returns (if you had this wrong on a previous homework, please reach out to see how to fix it), determine the confidence intervals of the population variance of these log-returns at the 60%, 90%, and 95% levels.

# Question 2 (Adapted from Stinerock)

A study of 450 families found that 212 out of the had to cut back recently on the purchase of big-ticket items over the past 6 months.

## a)

What is the 90% confidence interval estimate of the population proportion $p$ of the households that are cutting back?

## b)

What sample size would you recommend to achieve a margin of error of .03?

## c)

How large a sample size would be required to achieve a 99% confidence intervalestimate of $p$ with a margin of error of .03?

## d)

How large a sample size would be required to achieve a 99% confidence interval estimate of $p$ with a margin of error of .025?

# Question 3 (Taken from Mathematical Statistics and Data Analysis by John Rice)

Answer whether the following are true or false and why.  Note that the why part is also very important

# a)

The center of a 95% confidence interval for the population mean is a random variable

# b) 

A 95% confidence interval for $\mu$ contains the sample mean with probability .95

# c)

A 95% confidence interval contains 95% of the population

# d)

Out of one hunderd 95% confidence intervals for $\mu$, 95 will contain $\mu$.


