---
output: pdf_document

---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```



# QF112.  Homework #3.


## `r format(Sys.time(), "%Y-%m-%d")`

I pledge my honor that I have abided by the Stevens Honor System.

By filling out the following fields, you are signing this pledge.  No assignment will get credit without being pledged.

Name:

CWID:

Date:




```{r}
CWID = -1 #Place here your Campus wide ID number, this will personalize
#your results, but still maintain the reproduceable nature of using seeds.
#If you ever need to reset the seed in this assignment, use this as your seed
#Papers that use -1 as this CWID variable will earn 0's so make sure you change
#this value before you submit your work.
personal = CWID %% 10000
set.seed(personal)
```

It will be up to you to determine where you should use R code in this document.  You can easily add a new section of code by simply using copy/paste or typing it in yourself.  For your convenience, a blank section of code is provided below.

```{r}
# my response
```

# Question 1 (adapted from Stinerock: Statistics with R)

In 2013, the average level of debt from graduating students was 27,000 dollars.  We will assume this as the population mean with a standard deviation of 4500.  If we take a sample of 121 graduates, answer the following questions.

## a)

What is the probability that $\bar{x}$ will fall within 500 dollars of the population mean?

## b)

What is the probability that $\bar{x}$ will fall within 250 dollars of the population mean?

# Question 2 (adapted from Stinerock: Statistics with R)

If we assume that the percentage of people in the world who are left handed is 12\%, answer the following

## a) 
 If a sample of $n=400$ people is chosen at random, what is the probability that $\bar{p}$ is within .02 of $p$?
 
## b)

Answer the same question as in part a) but this time, assume that $n=800$.

# Question 3

Load in the data set that you created for homework 2 (consisting of the adjusted close prices for one year for two assets, which we'll arbitrarily label asset A and asset B).  we will be treating these data sets as the true population, so this is a finite population.  As a result, you will be sampling without replacement for this problem.  Answer the following:

## a)

Assuming that your data set is the true population, for asset A, determine the two population parameters, $\mu_A$ and $\sigma_A$. 

## b)

If you were to take a sample of $n=40$ values from this data set, what is the probability that $\bar{x_A}$ would be within 1 dollar of the population mean?

## c)

Generate 1000 samples of size $n=40$ from your data.  What percentage of these sample means are within 1 dollar of the population mean?  Does your answer agree with what you determined in part b)?  Why or why not?

## d)

Do part c) again, but this time use 10000 samples.

## e)

Using asset B, modify your data to determine when the stock increases in value.  To do this, use the sign and diff functions, which will result in a vector of $N-1$ values  These will be -1 for a decrease, 0 for the stock staying the same, and 1 for an increase.  Treat this new vector as your new population.  Let $p_B$ be the percentage of days in which the stock increases in value.

## f)
If you were to take a sample of $n=50$ values from this data set, what is the probability that $\bar{p_B}$ would be within 2 percent of the population proportion?

## g)
Generate 1000 samples of size $n=50$ from your data.  What percentage of these sample proportions are within 2 percent of the population percentage?  Does your answer agree with what you determined in part f)?  Why or why not?

## h)
Do part g) again, but this time use 10000 samples.



